%-------------------------
% Resume in Latex
% Author : Satyajit Samal
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{mathptmx}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{12pt}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      #3 & #4 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Satyajit Samal} \\ \vspace{5pt}
    \small {\raisebox{-0.1\height}{\scalebox{0.8}{\rotatebox[origin=c]{270}{\faPhone}}}} +91 9348569512 ~ {\raisebox{-0.1\height}\faMapPin} Bhubaneswar, Odisha - 751021 \\ 
    
    \vspace{5pt}
    
    \href{satyajitsamal.workmail@gmail.com}{\raisebox{-0.3\height}\faEnvelope \hspace{2pt}\underline{\textcolor{blue}{satyajitsamal.workmail@gmail.com}}} ~ 
    \href{https://satyajit-samal.vercel.app/}{\raisebox{-0.2\height}\faLaptopCode \hspace{2pt}\underline{\textcolor{blue}{Portfolio}}} ~ 
    \href{https://linkedin.com/in/satyajitsamal/}{\raisebox{-0.1\height}\faLinkedin \hspace{2pt}\underline{\textcolor{blue}{LinkedIn}}} ~
    \href{https://github.com/s-satyajit}{\raisebox{-0.1\height}\faGithub \hspace{2pt}\underline{\textcolor{blue}{GitHub}}}
    
    \vspace{6pt}
    
\end{center}



%-----------EDUCATION-----------
\section{\textrm{\scalebox{1.2}{E}DUCATION}}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Biju Pattanaik University of Technology}{Oct 2020 -- July 2024}
      {Bachelor of Technology in Computer Science}{Bhubaneswar, Odisha}
      \vspace{6pt}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------



\section{\textrm{\scalebox{1.2}{P}ROJECTS}}
    \vspace{-5pt}
    
    \resumeSubHeadingListStart
    
          
      \resumeProjectHeading
          {\textbf{LiveTalk - Multi User Chat Application} $|$ {React, Zustand, Firebase, Socket.IO } $|$ {
          \href{https://github.com/s-satyajit/multi-user-chatApp}{\raisebox{-0.\height}\faGithub\ \underline{\textcolor{blue}{GitHub}}} ~ 
          \href{https://multi-user-chat.vercel.app/}{\raisebox{-0.\height}\faLaptopCode\ \underline{\textcolor{blue}{Live}}}} ~
          \href{https://www.linkedin.com/feed/update/urn:li:activity:7271581170591502339/}{\raisebox{-0.\height}\faLaptop\ \underline{\textcolor{blue}{Preview}}}
          }
          {Dec 2024}
          \resumeItemListStart
            \resumeItem{Built a real-time chat app using React, Socket.IO, and Firebase for multi-user messaging and instant updates.}
            \resumeItem{Integrated Firebase Authentication for secure login and real-time data sync across devices.}
            \resumeItem{Optimized UI for seamless, intuitive messaging and real-time communication.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
          \resumeProjectHeading
          {\textbf{Hirrd - Job Portal Application} $|$ {React, Context API, TailwindCSS, Supabase, Radix} $|$ {
          \href{https://github.com/s-satyajit/hirrd-jobPortal}{\raisebox{-0.\height}\faGithub\ \underline{\textcolor{blue}{GitHub}}} ~ 
          \href{https://job-portal-eight-delta.vercel.app/}{\raisebox{-0.\height}\faLaptopCode\ \underline{\textcolor{blue}{Live}}}} ~
          \href{https://www.linkedin.com/feed/update/urn:li:activity:7269678588927336448/}{\raisebox{-0.\height}\faLaptop\ \underline{\textcolor{blue}{Preview}}}
          }
          {Dec 2024}
          \resumeItemListStart
            \resumeItem{Developed a job portal with React, Supabase, and Clerk, enabling users to create profiles and apply for jobs.}
            \resumeItem{Implemented Clerk authentication and used Supabase for efficient database management.}
            \resumeItem{Enhanced UI/UX with Shadcn UI and Radix UI for a responsive, user-friendly design.
}
          \resumeItemListEnd 
          \vspace{-13pt}
          
          \resumeProjectHeading
          {\textbf{TeamZen - Employee Management System} $|$ {React, Context API, Tailwind CSS}$|$ {
          \href{https://github.com/s-satyajit/employee-management-system}{\raisebox{-0.\height}\faGithub\ \underline{\textcolor{blue}{GitHub}}} ~ 
          \href{https://teamzen.vercel.app/}{\raisebox{-0.\height}\faLaptopCode\ \underline{\textcolor{blue}{Live}}}} ~
          \href{https://www.linkedin.com/feed/update/urn:li:activity:7274346311833853952/}{\raisebox{-0.\height}\faLaptop\ \underline{\textcolor{blue}{Preview}}}
          }
          {Dec 2024}
          \resumeItemListStart
            \resumeItem{Built an employee management system with React and Context API for tracking employee records.}
            \resumeItem{Implemented data persistence with localStorage, allowing employees' data to be stored and retrieved without requiring a backend, ensuring a fast and smooth user experience.}
            \resumeItem{Styled the application with Tailwind CSS, providing a clean, responsive design that adapts seamlessly across devices while maintaining a user-friendly interface.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{CodeStudio - Web Code Editor} $|$ {React, CodeMirror, ContextAPI, MaterialUI} $|$ {
          \href{https://github.com/s-satyajit/WebCodeEditor}{\raisebox{-0.\height}\faGithub\ \underline{\textcolor{blue}{GitHub}}} ~ 
          \href{https://web-code-editor-sigma.vercel.app/}{\raisebox{-0.\height}\faLaptopCode\ \underline{\textcolor{blue}{Live}}}} ~
          \href{https://www.linkedin.com/feed/update/urn:li:activity:7265341855377088512/}{\raisebox{-0.\height}\faLaptop\ \underline{\textcolor{blue}{Preview}}}
          }
          {Nov 2024}
          \resumeItemListStart
            \resumeItem{Leveraged CodeMirror for syntax highlighting and code formatting, improving readability and enhancing the user experience for developers.}
            \resumeItem{Enhanced the user experience with features like syntax highlighting, error detection.}
            \resumeItem{Styled with Material UI, ensuring a modern, responsive design that adapts across devices while offering an intuitive and user-friendly interface for seamless code editing.}
          \resumeItemListEnd
          \vspace{5pt}
          
    \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{\textrm{\scalebox{1.2}{E}XPERIENCE}}

  \resumeSubHeadingListStart

    \resumeSubheading
      {FluenceTech}{Dec 2022 -- Mar 2023}
      {Front-end Developer Intern}{Bhubaneswar, Odisha}
      \resumeItemListStart
        \resumeItem{Designed and developed responsive web interfaces using HTML, CSS, JavaScript, and React, ensuring seamless performance and accessibility across devices, including mobile and desktop.}
        \resumeItem{Translated Figma design mockups into interactive, feature-rich web pages, enhancing user engagement.}
        \resumeItem{Improved application responsiveness by implementing effective state management techniques and optimizing DOM manipulation for faster load times and smoother interactions.}
        \resumeItem{Worked closely with designers and back-end developers, aligning on functionality and aesthetics to deliver cohesive, user-focused solutions while maintaining consistency in design and performance.}
      \resumeItemListEnd
    \vspace{5pt}
  \resumeSubHeadingListEnd

\begin{}
  
\end{}

%-----------INVOLVEMENT---------------
\section{\textrm{\scalebox{1.2}{C}ERTIFICATE}}

    \resumeSubHeadingListStart
    \resumeSubheading
        {NullClass Certificate of Training $|$ \href{https://drive.google.com/file/d/1GZ8qfVwk2DCE8oYuyjaqF5XNRdcQWHjE/view}{\raisebox{0.09\height}{\scalebox{0.8}{\faFileContract}} \underline{\textcolor{Blue}{\textnormal{Drive Link}}}}}
        {May 2023}
        {HTML, CSS, JavaScript, React, NodeJS, MongoDB}
        {NullClass}
        \resumeItemListStart
            \resumeItem{Completed a comprehensive online training on Web Development, focusing on building a real-time website like StackOverflow.}
            \resumeItem{Gained hands-on experience in full-stack development, implementing real-time functionalities.}
        \resumeItemListEnd
    \vspace{5pt}
\resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{\textrm{\scalebox{1.2}{T}ECHNICAL \scalebox{1.2}{S}KILLS}}

 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Java, HTML/CSS} \\
     \textbf{Developer Tools}{: Linux, GitHub, CI/CD} \\
     \textbf{Technologies/Frameworks}{: React, Redux, Zustand, Tailwind CSS, Material UI, Node.js, Firebase, Appwrite} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
